Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2022-05-12 manuscript/manuscript.Rmd
update manuscript with review suggestions

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2
bibliography:
  - references.bib
  - GermanPolishpaper.bib
csl: vancouver.csl
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width = "100%", 
                      fig.pos = "H", out.extra = "")
library(kableExtra)
library(magrittr)
library(knitr)
```

@@

Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub. Until December 14th, 2020, these data were sourced from the European Centre for Disease Control [@ecdcDownloadHistoricalData2020]. After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021]. These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020).

@@

@@

At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble"). This "Hub ensemble" was retrospectively computed and excludes all our models. It therefore differs from the official Hub ensemble (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts. To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e. we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values >1 implying worse and values <1 implying better performance than the Hub ensemble). In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across for forecasts one to four weeks into the future (marked as 1 - 4 on the x axis). A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

@@

All forecasting approaches, including the Hub ensemble, were overconfident, i.e. they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)). Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons.

@@

Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \@ref(fig:performance-locations-rel)A and \@ref(fig:performance-locations-rel)G).

@@

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F. The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).

```{r}
caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. Points denote single forecasts scores, while the shaded area shows an estimated probability density. B: Distribution of WIS separate by country."
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

```{r agg-performance-ensemble, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
```

## Contribution to the Forecast Hub

@@

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.

@@

The strong performance of crowd forecasts in our study is in line with results from Farrow et al. who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers. One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts. Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting.

@@

NIB received funding from the Health Protection Research Unit (grant code NIHR200908). SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z). The work of JB was supported by the Helmholtz Foundation via the SIMCARD Information and Data Science Pilot Project. This research was partly funded by the National Institute for Health Research (NIHR) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research. The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care. BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859). EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688). AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID, and the Academy of Medical Sciences. SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z), and the NIHR (NIHR200908).

@@

@@

### Performance across locations in absolute terms
```{r}
caption <- "Visualisation of aggregate performance metrics across locations. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean further spread out forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals."
```

@@

```{r}
caption <- " Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions). A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean further spread out forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals."
```

@@

@@

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

@@

In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later. This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

@@

>>>>

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2 
bibliography:
  - references.bib
  - GermanPolishpaper.bib
csl: vancouver.csl
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width = "100%", 
                      fig.pos = "H", out.extra = "")

library(kableExtra)
library(magrittr)
library(knitr)
```

@@

Data on daily reported test positive cases and deaths linked to COVID-19 were provided by the organisers of the German and Polish Forecast hub. Until December 14th, 2020, these data were sourced from the European Centre for Disease Control [@ecdcDownloadHistoricalData2020]. After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@rkiRKICoronavirusSARSCoV22021]. These data are subject to reporting artefacts, (such as for example delayed case reporting in Poland on the 24th November, @forsal.plRozbieznosciStatystykachKoronawirusa2020), changes in reporting over time, and variation in testing regimes (for example in Germany from the 11th of November on, @aerzteblattSARSCoV2DiagnostikRKIPasst2020). The ECDC data as well as the data published by the Polish Ministry of Health were also subject to data revisions, although most of them (with a notable exception of a data update for October 12 2020 in Germany) only affected daily, not weekly data (see Figures \@ref(fig:daily-truth-update) and \@ref(fig:weekly-truth-update))

@@

The study was approved by the Observational / Interventions Research Ethics Committee at the London School of Hygiene & Tropical Medicine, LSHTM Ethics Reference: 22290.

@@

At all stages of the evaluation our forecasts were compared to the median ensemble of all *other* models submitted to the German and Polish Forecast Hub ("Hub ensemble"). This "Hub ensemble" was retrospectively computed and excludes all our models, leaving on average five ensemble member models (see details in Section \@ref(contributions-hub), as well as in Table \@ref(tab:table-ensemble-versions) and Figure \@ref(fig:num-ensemble-members) in the SI). What we call "Hub ensemble" in this article therefore differs from the "official Hub ensemble" (here called "hub-ensemble-realised") which included crowd forecasts as well as renewal model forecasts. 
To enhance interpretability of scores we mainly report WIS relative to the Hub ensemble in the main text, i.e. we divided the average scores for a given model by the average score achieved by the Hub ensemble on the same set of forecasts (with values >1 implying worse and values <1 implying better performance than the Hub ensemble). In addition to comparing our forecasts against the hub ensemble excluding our models, we also assessed the impact of our forecasts on the performance of the forecasting hub by recalculating separate versions of the Hub ensemble with only some (or all) of our forecasts included. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively.

@@

```{r}
caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \@ref(tab:score-table-2)). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores)), as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

@@

All forecasting approaches, including the Hub ensemble, were overconfident, i.e. they showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which had markedly shorter prediction intervals (i.e., narrower and more confident predictive distributions) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), the narrow forecast intervals led to forecasts which were severely overconfident (covering only 36% and 55% of all observations with the 50% and 90% prediction intervals of all forecasts made at a two week forecast horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)). Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly across forecast horizons. The crowd forecasts, on the other hand, showed a smaller bias than the renewal model, but were overconfident.

@@

Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figures \@ref(fig:performance-locations-rel)A, \@ref(fig:performance-locations-rel)G, \@ref(fig:performance-all-Germany), \@ref(fig:performance-all-Poland)).

@@

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F. The convolution model had a strong tendency to under-predict, with the magnitude of under-prediction steadily decreasing for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).

```{r}
caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. Points denote single forecasts scores, while the shaded area shows an estimated probability density. B: Distribution of WIS separate by country. Black squares indicate median and black circles mean scores."
```

@@

```{r}
caption <- "Visualisation of relative aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble. “Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but not the convolution model. A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance). C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble. E: Dispersion relative to the dispersion of the Hub ensemble. Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- orunderpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast relative to the Hub ensemble. H. Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
```

```{r agg-performance-ensemble-rel, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-v4.png")
```

## Contribution to the Forecast Hub {#contributions-hub}

@@

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the Hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.

@@

The strong performance of crowd forecasts in our study is in line with results from Farrow et al. who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this probably explains only part of the difference, and performance relative to the Hub ensemble strongly suggests that human insight is valuable when forecasting highly volatile and potentially hard-to-predict quantities such as case numbers. One potential explanation is that humans can have access to data that is not available to or hard to integrate into model-based forecasts. Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting which have less of an influence on weekly reporting.

@@

NIB received funding from the Health Protection Research Unit (grant code NIHR200908, https://www.nihr.ac.uk/). SA's work was funded by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/). The work of JB was supported by the Helmholtz Foundation (https://www.helmholtz.de/) via the SIMCARD Information and Data Science Pilot Project. This research was partly funded by the National Institute for Health Research (NIHR, https://www.nihr.ac.uk/) (16/137/109 & 16/136/46) using UK aid from the UK Government to support global health research. The views expressed in this publication are those of the author(s) and not necessarily those of the NIHR or the UK Department of Health and Social Care. BJQ is supported in part by a grant from the Bill and Melinda Gates Foundation (OPP1139859, https://www.gatesfoundation.org/). EvL acknowledges funding by the National Institute for Health Research (NIHR) Health Protection Research Unit (HPRU) in Modelling and Health Economics (grant number NIHR200908, https://www.nihr.ac.uk/) and the European Union's Horizon 2020 research and innovation programme - project EpiPose (101003688, https://ec.europa.eu/programmes/horizon2020/). AC acknowledges funding by the NIHR, the Sergei Brin foundation, USAID (https://www.usaid.gov/), and the Academy of Medical Sciences (https://acmedsci.ac.uk/). SF's work was supported by the Wellcome Trust (grant: 210758/Z/18/Z, https://wellcome.org/), and the NIHR (NIHR200908, https://www.nihr.ac.uk/).

@@

\beginsupplement

@@

### Performance in Germany

```{r}
caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Germany. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all-Germany, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-Germany-v4.png")
```

### Performance in Poland

```{r}
caption <- "Visualisation of aggregate performance metrics for forecasts one to four weeks into the future in Poland. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all-Poland, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-Poland-v4.png")
```

### Performance across locations in absolute terms
```{r}
caption <- "Visualisation of aggregate performance metrics across locations. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of WIS values."
```

@@

```{r}
caption <- "Visualisation of relative aggregate performance metrics across locations. A, B: mean weighted interval score (WIS) across locations (lower values indicate better performance). C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals. E: Dispersion. Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- orunderpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast. H. Standard deviation of WIS values."
```

@@

```{r}
caption <- "Visualisation of the absolute difference between the daily report data at the time and the data now. In Germany, there were zero cases and deaths reported on 2020-10-12, and only later 2467 cases and 6 deaths were added. Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
```

```{r daily-truth-update, fig.cap=caption}
knitr::include_graphics("../analysis/plots/daily-data-updates.png")
```

```{r}
caption <- "Visualisation of the relative difference between the weekly report data at the time and the data now. Apart from the data that was retrospectively added on 2020-10-12, data updates did not have a noticeable effect on weekly data (as shown in the forecasting application). Data were last accessed through the German and Polish Forecast Hub on May 10 2022."
```

```{r weekly-truth-update, fig.cap=caption}
knitr::include_graphics("../analysis/plots/weekly-data-updates.png")
```

@@

```{r distribution-scores-differences, fig.cap="Density plot with the difference in WIS between the Crowd forecast and the Hub ensemble (values below zero mean better performance of the Crowd forecasts)."}
knitr::include_graphics("../analysis/plots/difference-wis-crowd-ensemble.png")
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble. “Hub-ensemble” *excludes* all our models, Hub-ensemble-all *includes* all of our models, “Hub-ensemble-realised” is the actual hub-ensemble observed in reality, which includes the renewal model and the crowd forecasts, but ont the convolution model. Values (except for Bias) are computed as differences to the Hub ensemble which excludes our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A, B: mean weighted interval score (WIS) across horizons relative to the Hub ensemble (lower values indicate better performance). C, D: Empirical coverage of the 50\\% and 90\\% prediction intervals minus empirical coverage observed for the Hub ensemble. E: Dispersion relative to the dispersion of the Hub ensemble. Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- orunderpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast relative to the Hub ensemble. H. Standard deviation of all WIS values for different horizons relative to the Hub ensemble."
```

@@

In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later. This sensitivity shows performance of all models restricted to the period from December 14 2020 until March 1st 2021 where all models were available.

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from December 14th 2020 on where all models were available. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

@@

## Comparison of crowd forecasts and application baseline

```{r compare-forecasters, fig.cap="Crowd forecasts and baseline shown in the application for a two week horizon. Shown are the 90\\% and 50\\% prediction intervals as well as the median (in order of increasing opacity). For any given point in time, the baseline shown in red is what forecasters saw when they opened the app (the baseline shown was constant across all forecast horizons)."}
knitr::include_graphics("../analysis/plots/comparison-forecast-interals.png")
```
